{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-26 thesis/quicksand.tex
figure captions:

\begin{figure}[t]
	\begin{center}
		\includegraphics[width=0.87\textwidth]{nondets.pdf}
	\end{center}
	\caption[Nondeterministic data-race preemption points are required to find some bugs.]
	{Nondeterministic data-race preemption points are required to find some bugs.
	Requiring stateless model checking integration to identify to begin with,
	incorporating these races as new preemption points
	allowed Quicksand to find
	% lhb: 127.77%
	% phb: 191.30%
	128\% (Limited Happens-Before) to 191\% (Pure Happens-Before) as many data-race bugs
	compared to using single-pass candidates alone.
	}
	\label{fig:dr-falsenegs}
\end{figure}

>>>>

\begin{figure}[t]
	\begin{center}
		\includegraphics[width=0.87\textwidth]{nondets.pdf}
	\end{center}
	\caption[Some bugs require nondeterministic data-race preemption points to expose.]
	{Some bugs require nondeterministic data-race preemption points to expose.
	Incorporating these data races,
	which are not observed under single-pass analysis,
	%which stateless model checking integration to identify to begin with,
	as new preemption points
	allowed Quicksand to find
	% lhb: 127.77%
	% phb: 191.30%
	128\% (Limited Happens-Before) to 191\% (Pure Happens-Before) as many data-race bugs
	compared to using single-pass candidates alone.
	}
	\label{fig:dr-falsenegs}
\end{figure}

### 2018-12-26 thesis/tm.tex
figure captions:

\begin{figure}[h]
	\begin{center}
		\begin{tabular}{ll}
		%\texttt{void count() \{} \\
		%\texttt{~~~~for (int i = 0; i < 1000; i++) \{} \\
		& \texttt{\ctype{bool} prevent\_transactions = \const{false};} \\
		\\
		0 & \texttt{\flow{while} (prevent\_transactions) \flow{continue};} \\
		1 & \texttt{\flow{if} ((status = \call{\_xbegin}()) == \const{\_XBEGIN\_STARTED}) \{} \\
		2 & \texttt{~~~~\flow{if} (prevent\_transactions)} \\
		3 & \texttt{~~~~~~~~\call{\_xabort}();} \\
		4 & \texttt{~~~~x++;} \\
		5 & \texttt{~~~~\call{\_xend}();} \\
		6 & \texttt{\} \flow{else} \{} \\
		7 & \texttt{~~~~\call{mutex\_lock}(\&m);} \\
		8 & \texttt{~~~~prevent\_transactions = \const{true};} \\
		9 & \texttt{~~~~x++;} \\
		A & \texttt{~~~~prevent\_transactions = \const{false};} \\
		B & \texttt{~~~~\call{mutex\_unlock}(\&m);} \\
		C & \texttt{\}} \\
		%\texttt{~~~~\}} \\
		%\texttt{\}} \\
		\end{tabular}
	\end{center}
	\caption[Variant of the program in \Cref{fig:htm-example-reproduced}.]
		{Variant of the program in \Cref{fig:htm-example-reproduced},
		with additional synchronization to protect the failure path from the transactional path.
		The optional line 0 serves to prevent a cascade of failure paths
		for the sake of performance
		by allowing threads to wait until transacting is safe again.}
	\label{fig:htm-fixed}
\end{figure}

>>>>

\begin{figure}[h]
	\begin{center}
		\begin{tabular}{ll}
		%\texttt{void count() \{} \\
		%\texttt{~~~~for (int i = 0; i < 1000; i++) \{} \\
		& \texttt{\ctype{bool} prevent\_transactions = \const{false};} \\
		\\
		0 & \texttt{\flow{while} (prevent\_transactions) \flow{continue};} \\
		1 & \texttt{\flow{if} ((status = \call{\_xbegin}()) == \const{\_XBEGIN\_STARTED}) \{} \\
		2 & \texttt{~~~~\flow{if} (prevent\_transactions)} \\
		3 & \texttt{~~~~~~~~\call{\_xabort}();} \\
		4 & \texttt{~~~~x++;} \\
		5 & \texttt{~~~~\call{\_xend}();} \\
		6 & \texttt{\} \flow{else} \{} \\
		7 & \texttt{~~~~\call{mutex\_lock}(\&m);} \\
		8 & \texttt{~~~~prevent\_transactions = \const{true};} \\
		9 & \texttt{~~~~x++;} \\
		A & \texttt{~~~~prevent\_transactions = \const{false};} \\
		B & \texttt{~~~~\call{mutex\_unlock}(\&m);} \\
		C & \texttt{\}} \\
		%\texttt{~~~~\}} \\
		%\texttt{\}} \\
		\end{tabular}
	\end{center}
	\caption[More correct version of the program in \Cref{fig:htm-example-reproduced}.]
		{More correct version of the program in \Cref{fig:htm-example-reproduced},
		with additional synchronization to protect the failure path from the transactional path.
		The optional line 0 serves to prevent a cascade of failure paths
		for the sake of performance
		by allowing threads to wait until transacting is safe again.}
	\label{fig:htm-fixed}
\end{figure}
